---
title: "Rise and fall"
author: "Simon Gabay"
date: "2023-02-06"
output:
  html_document:
    highlight: pygments
    toc: true
    toc_float:
      toc_collapsed: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/Users/gabays/github/BirthOfStyle")
```

# 1. Preparation

Set working directory

```{r, message=FALSE}
# change this value if needed
setwd("/Users/gabays/github/BirthOfStyle")
getwd()
```

Load packages

```{r, message=FALSE}
if(!require("ggplot2")){
  install.packages("ggplot2")
  library(ggplot2)
}
if(!require("roll")){
  install.packages("roll")
  library(roll)
}
if(!require("purrr")){
  install.packages("purrr")
  library(purrr)
}
if(!require("stylo")){
  install.packages("stylo")
  library(stylo)
}
```

Load external functions

```{r}
source("./R/functions.R")
```

Load previously computed data

```{r}
load("./R/RiseAndFall.RData")
```

# 2. Set up

## 2.1 As 3-grams

Get Metadata and corpus as 3-grams

```{r}
#Metadata
metadata = read.csv(file="./metadata.csv", sep=",", header = TRUE, row.names = 1, stringsAsFactors=T)
metadata = metadata[sort(rownames(metadata)), ]
#data
data =  read.csv(file="./feats_tests_n3_k_5000.csv", sep=",", header = TRUE, row.names = 1, stringsAsFactors=T)
```

We compute de distribution: which 3grams are relevant?

```{r}
dist = colSums(data[,3:ncol(data)])
plot(dist,type = "l")
```

We work with the 2000 most frequent 3grams -- after that the curve is totally flat

```{r}
d <- data[,3:2003]
```

We normalise the vectors

```{r}
d <- t(d)
#normalisation
d <- normalisations(d)
```

We add the metadata

```{r}
# we add the metadata
control<-rbind(rownames(metadata),colnames(d))
# we control that we have similar values
head(t(control))
tail(t(control))
```

## 2.2 As plain texts (beta)

Alternative: loading plays in plain text (for later)

```{r, message=FALSE}
corpus<-list()
#Get the list of all txt files
TxtFiles <- list.files(path = "txt",pattern = "txt$")
#Loop over all files
for(x in TxtFiles){
  #Get the path
  FullPath <- paste("txt", x, sep="/")
  #Get the name (drop .txt extension)
# TextName <- sub("\\.txt", "", x)
  #Get the text in the file
#  FullText <- suppressWarnings(read.csv(FullPath, header = FALSE, sep = "\n", fileEncoding="UTF-8"))
  FullText <- suppressWarnings(readLines(FullPath))
    #Append the text to the corpus
  corpus<-append(corpus,FullText)
}
View(corpus)
```

We transform the loaded texts into minable data

```{r}
#tokenisation
corpus.tok = lapply(corpus, txt.to.words2)
#Counting frequency of tokens
corpus.tok.list = make.frequency.list(corpus.tok)
#Transform frequency into a table
corpus.tok.list.freq=make.table.of.frequencies(corpus.tok, corpus.tok.list, relative = F)
#I name columns
row.names(corpus.tok.list.freq)=TxtFiles
#I save a copy
write.csv(corpus.tok.list.freq, file = "corpus.bench.tok.list.freq.csv",row.names=TRUE)
#Convert table into dataframe
corpus.tok.list.freq = as.data.frame(read.csv(file="corpus.bench.tok.list.freq.csv", sep = ",", header = TRUE, row.names=1, quote = '\"'))
#transposition (rows become columns)
corpus.tok.list.freq = t(corpus.tok.list.freq)
#normalisation
corpus.tok.list.freq = normalisations(corpus.tok.list.freq)
#Displaying the dataframe
View(corpus.tok.list.freq)
```

# 3 Experiments

## 3.1 Tests

### 3.1.1 generic value of 3-grams

We control that 3-grams do identify genres

```{r, fig.width=7, fig.height=7}

distToTragedy <- DistToCentroid(d, centroid = rowMeans(d[, metadata[, "Genre"] == "tragedy"]))

distToComedy <- DistToCentroid(d, centroid = rowMeans(d[, metadata[, "Genre"] == "comedy"]))

m <- cbind(distToTragedy, distToComedy)
colnames(m) <- c("DistTragedyCentroid","DistComedyCentroid")

#create transparent color
mycol <- t_col("white", perc = 100, name = "transparent")

#fix colors
colors <- metadata[, "Genre"]
levels(colors) = c("transparent","blue", "transparent", "transparent", "transparent", "transparent", "transparent", "transparent", "transparent", "red", "transparent", "transparent")
#plot
plot(m, col=as.character(colors))
legend(18, 38, c("comedy", "tragedy"),col=c("blue", "red"),pch=1)
grid(nx = NULL, ny = NULL,
     lty = 1,      # Grid line type
     col = "gray", # Grid line color
     lwd = 1)      # Grid line width
# text(m[, 1], m[, 2], labels=row.names(m), cex= 0.1) # To add the name of the plays

#Save the image
png("./R/images/clusters.png", width = 2500, height = 2000, res=300) 
plot(m, col=as.character(colors))
legend(18, 38, c("comedy", "tragedy"),col=c("blue", "red"),pch=1)
grid(nx = NULL, ny = NULL, lty = 1, col = "gray", lwd = 1)
dev.off() 

```

### 3.1.2 Within inertia of the two clusters

```{r}
#Get all possible genres
levels(metadata[, "Genre"])
#Get genre of all plays
clusters <- metadata[, "Genre"]
levels(clusters) <- c(1:13)

#Compute inertia
clusterInertia(t(d), as.numeric(clusters))
```

### 3.1.3 Centroid distance

Comedy

```{r}
comedies = d[, metadata[, "Genre"] == "comedy"]
comediesToCentroid = DistToCentroid(comedies, method="manhattan")

summary(comediesToCentroid)
boxplot(comediesToCentroid)
# Most typical comedies
head(comediesToCentroid[order(comediesToCentroid[, 1]),])
# Less typical comedies
tail(comediesToCentroid[order(comediesToCentroid[, 1]),])
```

```{r}
tragedies = d[, metadata[, "Genre"] == "tragedy"]
tragediesToCentroid = DistToCentroid(tragedies, method="manhattan")

summary(tragediesToCentroid)
boxplot(tragediesToCentroid)
# Most typical comedies
head(tragediesToCentroid[order(tragediesToCentroid[, 1]),])
# Less typical comedies
tail(tragediesToCentroid[order(tragediesToCentroid[, 1]),])
```

## 3.2 Evolution of tragedy

### 3.2.1 With 3-grams

```{r}
tragedies <- d[, metadata[, "Genre"] == 'tragedy' & metadata[, "Date"] <1800 & metadata[, "Date"] >1500]
tragediesToCentroid = DistToCentroid(tragedies, method="manhattan")
```

```{r}
evoCentroid<-cbind(tragediesToCentroid,metadata[metadata$Genre=='tragedy' & metadata[, "Date"] <1800 & metadata[, "Date"] >1500, ])
vizEvoCentroid <- ggplot(data = evoCentroid, mapping = aes(x = Date, y = DistToCentroid))+
  geom_point(stat = "summary", fun = "mean")+ 
  geom_smooth(method = loess, size = 1)+ theme_bw()
ggsave("./R/images/tragedy3.png", plot=vizEvoCentroid, width = 2500, height = 2000, units = "px", dpi = 300)
vizEvoCentroid
```

### 3.2.2 With words

```{r}
tragedies <- corpus.tok.list.freq[, metadata[, "Genre"] == 'tragedy' & metadata[, "Date"] <1800 & metadata[, "Date"] >1500]
tragediesToCentroid = DistToCentroid(tragedies, method="manhattan")
```

```{r}
evoCentroid<-cbind(tragediesToCentroid,metadata[metadata$Genre=='tragedy' & metadata[, "Date"] <1800 & metadata[, "Date"] >1500, ])
vizEvoCentroid <- ggplot(data = evoCentroid, mapping = aes(x = Date, y = DistToCentroid))+
  geom_point(stat = "summary", fun = "mean")+ 
  geom_smooth(method = loess, size = 1)+ theme_bw()
ggsave("./R/images/tragedyW.png", plot=vizEvoCentroid, width = 2500, height = 2000, units = "px", dpi = 300)
vizEvoCentroid
```

## 3.3 Evolution of comedy

### 3.3.1 With 3-grams

```{r}
tragedies <- d[, metadata[, "Genre"] == 'comedy' & metadata[, "Date"] <1800 & metadata[, "Date"] >1500]
tragediesToCentroid = DistToCentroid(tragedies, method="manhattan")
```

```{r}
evoCentroid<-cbind(tragediesToCentroid,metadata[metadata$Genre=='comedy' & metadata[, "Date"] <1800 & metadata[, "Date"] >1500, ])
vizEvoCentroid <- ggplot(data = evoCentroid, mapping = aes(x = Date, y = DistToCentroid))+
  geom_point(stat = "summary", fun = "mean")+ 
  geom_smooth(method = loess, size = 1)+ theme_bw()
ggsave("./R/images/comedy3.png", plot=vizEvoCentroid, width = 2500, height = 2000, units = "px", dpi = 300)
vizEvoCentroid
```

### 3.3.2 With words

```{r}
tragedies <- corpus.tok.list.freq[, metadata[, "Genre"] == 'comedy' & metadata[, "Date"] <1800 & metadata[, "Date"] >1500]
tragediesToCentroid = DistToCentroid(tragedies, method="manhattan")
```

```{r}
evoCentroid<-cbind(tragediesToCentroid,metadata[metadata$Genre=='comedy' & metadata[, "Date"] <1800 & metadata[, "Date"] >1500, ])
vizEvoCentroid <- ggplot(data = evoCentroid, mapping = aes(x = Date, y = DistToCentroid))+
  geom_point(stat = "summary", fun = "mean")+ 
  geom_smooth(method = loess, size = 1)+ theme_bw()
ggsave("./R/images/comedyW.png", plot=vizEvoCentroid, width = 2500, height = 2000, units = "px", dpi = 300)
vizEvoCentroid
```

## 3.4 Distance to auctorial centroid vs generic centroid

We select all the authors with more than 3 plays in the dataset

```{r}
#all authors
n_occur <- data.frame(table(metadata$Author))
# Remove forst row (author empty value)
n_occur<-n_occur[-1,]

#more than 4 times
multiples <- n_occur[n_occur$Freq > 2,]
#transform df into vector
multiples <- multiples$Var1
#number of authors
length(multiples)
```

We select all the authors who have more than 1 comedy

```{r}
authorsSelected=c()
for (x in multiples){
  results <- as.data.frame(metadata[metadata$Genre == 'comedy' & metadata$Author == x,])
  if(nrow(results)>2){
  authorsSelected<-append(authorsSelected,x)
  }
}
```

We compute the distance to the centroid of the author, the centroid of the genre and the distance between both:

```{r}
#create an empty df to store results
df2=data.frame(matrix(ncol = 7, nrow = 0))

#get name of plays
plays<-rownames(metadata)
#prepare to iterate
incr<-0

#loop over plays
for (x in plays){
  #increment
  incr<-incr+1
  #get author name
  author <- metadata[incr,2]
  #get genre
  genre<-metadata[incr,4]
  #get date
  date<-metadata[incr,3]
  #if author has written multiple texts present in the corpus and genre is known
   if (author %in% authorsSelected==TRUE & genre =='comedy' & date>1500 & date<1800){
    #get the data of all the plays of an author
    authorData = d[, metadata[, "Author"] == author & metadata[, "Genre"] == genre]
#    authorData = d[, metadata[, "Author"] == author]
    #get all the plays of the same genre
#    genreData = d[, metadata[, "Genre"] == genre & metadata[, "Date"]]
    genreData = d[, metadata[, "Genre"] == genre & metadata[, "Date"] <date+30 & metadata[, "Date"] >date-30]
    #compute distance to centroid of the author
    authorToCentroid = as.data.frame(DistToCentroid(authorData, method="manhattan"))
    #compute distance to centroid of the genre
    genreToCentroid = as.data.frame(DistToCentroid(genreData, method="manhattan"))
    #get the distance of the play to the author
    playDistAuthor<-authorToCentroid[x,]
    #get the distance of the play to the genre
    playDistGenre<-genreToCentroid[x,]
    #diff author genre (rounded)
    distance<- round(euclidean(playDistGenre,playDistAuthor), digits=3)
    #distance<-round(playDistGenre-playDistAuthor, digits = 2)
    #save the result if value is not zero (problem occurred)
    control<-playDistAuthor!=''
    if (is.na(control)==FALSE){
      results<-c(x,author,genre,date,distance,playDistAuthor,playDistGenre)
      df2<-rbind(df2,results)
    }
  }
}
#give a name to the columns
x <- c("play","author", "genre","date","distance", "distance2author","distance2genre")
labelPoints<-rownames(df2)
colnames(df2) <- x
```

### 3.3.1 Distance to author

```{r}
vizEvoCentroid <- ggplot(data = df2, mapping = aes(x = as.numeric(date), y = as.numeric(distance2author), label=rownames(df2)))+
  geom_point(stat = "summary", fun = "mean")+ 
  geom_smooth(method = loess, size = 1)+
  xlab("Date") + ylab("Distance to the author")+
  theme_bw() #+geom_text(hjust=0, vjust=0, size=3)
ggsave("R/images/distance2author.png", plot=vizEvoCentroid, width = 2500, height = 2000, units = "px", dpi = 300)
vizEvoCentroid
```

### 3.4.2 Distance to genre

```{r}
vizEvoCentroid <- ggplot(data = df2, mapping = aes(x = as.numeric(date), y = as.numeric(distance2genre), label=rownames(df2)))+
  geom_point(stat = "summary", fun = "mean")+ 
  geom_smooth(method = loess, size = 1)+
  xlab("Date") + ylab("Distance to the genre") +
  theme_bw() #+geom_text(hjust=0, vjust=0, size=3)
ggsave("R/images/distance2genre.png", plot=vizEvoCentroid, width = 2500, height = 2000, units = "px", dpi = 300)
vizEvoCentroid
```

### 3.4.3 Distance between the two centroids

```{r}
vizEvoCentroid <- ggplot(data = df2, mapping = aes(x = as.numeric(date), y = as.numeric(distance), label=rownames(df2)))+
  geom_point(stat = "summary", fun = "mean")+ 
  geom_smooth(method = loess, size = 1)+
  xlab("Date") + ylab("Distance")+
  theme_bw() #+geom_text(hjust=0, vjust=0, size=3)
ggsave("R/images/spread.png", plot=vizEvoCentroid, width = 2500, height = 2000, units = "px", dpi = 300)
vizEvoCentroid
```
Controlling variance

```{r}
# with 4 plays
#x <- 1:71
x <- 1:nrow(df2)
y<-roll_var(as.numeric(df2$distance), width = 30, min_obs = 1)
lo <- loess(y~x)
plot(x,y,xlab="index", ylab="variance")
lines(predict(lo), col='red', lwd=2)
png("./R/images/variance2.png", width = 850, height = 600) 
plot(x,y,xlab="index", ylab="variance")
lines(predict(lo), col='red', lwd=2)
dev.off() 
```

